### 2024-08-14 CV2/papers.tex
arxiv button for preprints

\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{arXiv preprint arXiv:2405.18031}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized Finite-Sum Optimization over Time-Varying Networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2402.02490}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2307.12946}{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2307.12946}, 2023.

@@

\textbf{\href{https://arxiv.org/abs/2212.14439}{An optimal algorithm for strongly convex min-min optimization}} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky). \textit{arXiv preprint arXiv:2212.14439}, 2022.

@@

\textbf{\href{https://arxiv.org/abs/2206.08303}{On scaled methods for saddle point problems}} (Aleksandr Beznosikov, Aibek Alanov, Dmitry Kovalev, Martin Takac, Alexander Gasnikov). \textit{arXiv preprint arXiv:2206.08303}, 2022.

@@

\textbf{\href{https://arxiv.org/abs/2102.07758}{Decentralized distributed optimization for saddle point problems}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov). \textit{arXiv preprint arXiv:2102.07758}, 2021.

@@

\textbf{\href{https://arxiv.org/abs/2002.11337}{Fast linear convergence of randomized BFGS}} (Dmitry Kovalev, Robert M Gower, Peter Richtarik, Alexander Rogozin). \textit{arXiv preprint arXiv:2002.11337}, 2020.

@@

\textbf{\href{https://arxiv.org/abs/1912.09925}{Distributed fixed point methods with compressed iterates}} (Selim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtarik, Adil Salim, Martin Takac). \textit{arXiv preprint arXiv:1912.09925}, 2019.

@@

\textbf{\href{https://arxiv.org/abs/1912.01597}{Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates}} (Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik). \textit{arXiv preprint arXiv:1912.01597}, 2019.

>>>>

\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{arXiv preprint arXiv:2405.18031}, 2024.

@@

\textbf{Decentralized Finite-Sum Optimization over Time-Varying Networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2402.02490}, 2024.

@@

\textbf{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2307.12946}, 2023.

@@

\textbf{An optimal algorithm for strongly convex min-min optimization} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky). \textit{arXiv preprint arXiv:2212.14439}, 2022.

@@

\textbf{On scaled methods for saddle point problems} (Aleksandr Beznosikov, Aibek Alanov, Dmitry Kovalev, Martin Takac, Alexander Gasnikov). \textit{arXiv preprint arXiv:2206.08303}, 2022.

@@

\textbf{Decentralized distributed optimization for saddle point problems} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov). \textit{arXiv preprint arXiv:2102.07758}, 2021.

@@

\textbf{Fast linear convergence of randomized BFGS} (Dmitry Kovalev, Robert M Gower, Peter Richtarik, Alexander Rogozin). \textit{arXiv preprint arXiv:2002.11337}, 2020.

@@

\textbf{Distributed fixed point methods with compressed iterates} (Selim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtarik, Adil Salim, Martin Takac). \textit{arXiv preprint arXiv:1912.09925}, 2019.

@@

\textbf{Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates} (Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik). \textit{arXiv preprint arXiv:1912.01597}, 2019.
